Homework 3: The Florentine Wedding dataset

### 2022-02-10 _academics/ps753-hw3/ps753-hw3.Rmd
Add code fold options

---
title: "Homework 3: The Florentine Wedding dataset"
description: |
  A first-look network analysis
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-09
output:
  distill::distill_article:
    self_contained: false
categories:
  - r
  - social networks
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.height = 8
)
library(network)
library(igraph)
library(tidyverse)

data(flo)
ntwk.ig <- graph_from_adjacency_matrix(flo)

@@

ntwk.indegree_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "in")$centralization
ntwk.outdegree_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "out")$centralization
ntwk.total_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "total")$centralization
```

>>>>

---
title: "Homework 3: The Florentine Wedding dataset"
description: |
  A first-look network analysis
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-09
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
categories:
  - r
  - social networks
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 8,
	message = FALSE,
	warning = FALSE
)
library(network)
library(igraph)
library(tidyverse)
```

```{r}
data(flo)
ntwk.ig <- graph_from_adjacency_matrix(flo)

@@

ntwk.indegree_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "in")$centralization
ntwk.outdegree_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "out")$centralization
ntwk.total_centralization <- centr_degree(ntwk.ig, loops = FALSE, mode = "total")$centralization
```
</details>
